---
output: github_document
---

```{r, echo = FALSE}
version <- as.vector(read.dcf('DESCRIPTION')[, 'Version'])
version <- gsub('-', '.', version)
```

[![R-CMD-check](https://github.com/tsmodels/tsmethods/workflows/R-CMD-check/badge.svg)](https://github.com/tsmodels/tsmethods/actions)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](/commits/master)
[![packageversion](https://img.shields.io/badge/Package%20version-`r version`-orange.svg?style=flat-square)](commits/master)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/tsmethods)](https://cran.r-project.org/package=tsmethods)


```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# tsmethods

Foundation packages with general methods/classes used by other **tsmodels** packages 
as well as plotting for prediction and distribution classes conforming to the 
current probabilistic framework. Also includes functions for ensembling using 
a copula methodology.

## Installation

For installation instructions and vignettes for **tsmodels** packages, 
see https://tsmodels.github.io/.

## To Do

[x] Create tsequation for each of the packages to generate latex output of both the generic model equation used as well as option for populating with actual parameter values.

[x] Switch to using either ggplot2 or plotly for plotting output of tsmodel.predict and tsmodel.distribution.

[x] Check consistency of colors and output for plots across packages (for estimated object).

[x] Check consistency of summary output across packages (for estimated object).

[x] Create tsanimate method for animating walkthrough in tsbacktest output.

[x] Convert documentation to roxygen [ongoing]

[x] Enhance tsconvert method to generate SEM model from MEM and add appendix in vignette for proof based on Casals et al. paper (James Nesbit).